On the properties of discs around accreting brown dwarfs

### 2010-06-30 BDD_submit/paper.tex
More adjustment this time to text pertaining to Figure 7
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2334 25464f21-6099-402c-b30a-640f1d40d38b

The changes in flux with inclination will clearly lead to changes in
the observed magnitudes and colours with inclination. Figure
\ref{flare_mag} shows the $M_V$ and $M_J$ magnitudes in the top
and bottom panels respectively. The magnitudes are then marked as
crosses as a function of inclination. The systems shown in both panels
have an age of 1 Myr, mass of $0.04M_{\odot}$, rotation rates of 0.5
and an areal coverage of 10\%. The systems with accretion rates of
\logmdot = $-$12, $-$9 and $-$7 are shown in black, red and blue,
respectively. The panels also show the system with the highest
accretion rate but with a rotation rate of 5 days as a dashed
line. The vertical dotted lines in the lowest panel simply illustrate
the total change in magnitude, over the shown inclination range.

>>>>

The changes in flux with inclination will clearly lead to changes in
the observed magnitudes and colours with inclination. Figure
\ref{flare_mag} shows the $M_V$ and $M_J$ magnitudes in the top and
bottom panels respectively. The magnitudes are then marked as crosses
as a function of inclination. The systems shown in both panels have an
age of 1 Myr, mass of $0.04M_{\odot}$, rotation rates of 0.5 and an
areal coverage of 10\%. The systems with accretion rates of \logmdot =
$-$12, $-$9 and $-$7 are shown in black, red and blue,
respectively. The panels also show the system with the highest
accretion rate but with a rotation rate of 5 days as a dashed
line. The vertical dotted lines in the lowest panel simply illustrate
the inclinations of 71$^{\circ}$ and 56$^{\circ}$.
